---
title: "fyp_study1_stats"
author: "Jonas Schöne"
date: "22 April 2019"
output: html_document
---

```{r}
library(tidyverse)
library(psych)
```

### reading the file

```{r}
df <- read.csv( file= "data/data_questionnaire_1.csv")

#D:/DownloadsDesktop/Desktop/Stanford/Bachelr-Thesis/fyp_study1/
```

### Demografics

```{r}
#Distribuition of age and gender

meanAge <- mean(df$age)

meanAgeGender <- describeBy (df$age,group = df$gender)


```


### Item Analysis PRSRI (PROMIS sleep-related impairment)

```{r}
promis.df <- df %>% 
  select(prsri_1:prsri_8)

alpha(promis.df)

cor.test(df$prsri_all, df$age)

DistrPromisGender <- describeBy (df$prsri_all,group = df$gender)
```

###psqi - Pittsburgh sleep quality index

```{r}
psqi.df <- df %>% 
  select(psqi_sq_c1,psqi_latency_c2,psqi_duration_c3,psqi_sf_c4)

### Componenten Consistency
alpha(psqi.df)

x <- na.omit(df$psqi_time_in_bed_h)
hist(x,prob=TRUE,main="Normal density + histogram")
  lines(density(x),lty="dotted",col="red")
  
SleepQualityDes <- describe(df$psqi_sq_c1)
SleepLatencyDes <- describe(df$psqi_latency_c2)
SleepDurationDes <- describe(df$psqi_duration_c3)
SleepEffeciencyDes <- describe(df$psqi_sf_c4)
PSQItotalDes <- describe(df$psqi_total)
DistrPSQIGender <- describeBy (df$psqi_total,group = df$gender)

```

### morningness eveningness questionnaire (meq)

```{r}
MorEvenDes <- describe(df$meq_19)
```
###: emotion regulation questionnaire frequency (erqf) + DISTRACTION #### FREQUENCY

```{r}
erqf.df <- df %>% 
  select(erqf_total_rap,erqf_total_sup, erqdf_total_dis)

DistrFreqRapGender <- describeBy (df$erqf_total_rap,group = df$gender)
DistrFreqSupGender <- describeBy (df$erqf_total_sup,group = df$gender)
DistrFreqDisGender <- describeBy (df$erqdf_total_dis,group = df$gender)

### Componenten Consistency
alpha(erqf.df)
```
###### Emotion regulation questionnaire capacity### EFFICACY

```{r}
erqse.df <- df %>% 
  select(erqse_total_rap,erqse_total_sup, erqse_total_dis)

DistrEffRapGender <- describeBy (df$erqse_total_rap,group = df$gender)
DistrEffSupGender <- describeBy (df$erqse_total_sup,group = df$gender)
DistrEffDisGender <- describeBy (df$erqdf_total_dis,group = df$gender)

### Componenten Consistency
alpha(erqse.df)
```
Interestingly, Efficacy is highly intercorrelated, whereas frequency is not

### Perth Reactivity Scale (PRS) ### REACTIVITY

```{r}
PERS.df <- df %>% 
  select(participant, starts_with("pers_pos"), starts_with("pers_neg"))

DistrPersPosGender <- describeBy (df$pers_pos_total,group = df$gender)
DistrPersNegGender <- describeBy (df$pers_neg_total,group = df$gender)

```
### Hypothesis Testing

(1)Zero-order correlations will be obtained among measures of sleep quality, sleep-related impairment, emotional reactivity

```{r}

## Sleep Quality (PSQI) and Reacticity (PERS) 
hyp1_1 <- df %>% 
  select(psqi_sq_c1, psqi_latency_c2, psqi_duration_c3, psqi_sf_c4, starts_with("pers_pos"), starts_with("pers_neg"), )

corr.test (hyp1_1)
cor.test (df$psqi_total, df$pers_neg_total)
cor.test (df$psqi_total, df$pers_pos_total)

## Impairment (PROMIS) and Reactivity(PERS)
hyp1_2 <- df %>%
  select(starts_with("pers_pos"), starts_with("pers_neg"), prsri_all)

corr.test (hyp1_2)
cor.test (df$prsri_all, df$pers_neg_total)
cor.test (df$prsri_all, df$pers_pos_total)
```
Seems like that Trait Sleep Quality can predict negative intensity and activation in bivariate correlations, but not positive.
Same seems to be the case for impairment. It is only related to the negative aspects.
Since negative items share tons of variance setp-wise regression needs to be done in order to say, which one is the major contributor.

(2)	Zero-order correlations will be obtained among measures of sleep quality, sleep-related impairment, emotion regulation frequency and self-efficacy

```{r}
## Sleep Quality (PSQI) and ERF
hyp2_1 <- df %>% 
  select(psqi_total, erqf_total_rap,erqf_total_sup, erqdf_total_dis)

corr.test (hyp2_1)

### Sleep Quality (PSQI) and ER-Selfefficacy

hyp2_2 <- df %>% 
  select(psqi_total, erqse_total_rap,erqse_total_sup, erqse_total_dis)

corr.test (hyp2_2)

### Sleep-Impairment (PROMIS) and ERF 

hyp2_3 <- df %>% 
  select(prsri_all, erqf_total_rap,erqf_total_sup, erqdf_total_dis)

corr.test (hyp2_3)

### Sleep-Impairment (PROMIS) and ER-Selfefficacy 

hyp2_4 <- df %>% 
  select(prsri_all, erqse_total_rap,erqse_total_sup, erqse_total_dis)

corr.test (hyp2_4)
```
There is not much to find for emotion regulation and Sleep Quality.
PSQI with Reappraisal but I dont know why? Probably, nothing that I would talk to much about

### Habitual Sleeptime and efficacy and Emotion Regulation
### Habitual sleep an ER reactivity

```{r}
## Sleep Duration and ERF
hyp3_1 <- df %>% 
  select(psqi_duration_c3, erqf_total_rap,erqf_total_sup, erqdf_total_dis)

corr.test (hyp3_1)

### Sleep Duration and ER-Selfefficacy

hyp3_2 <- df %>% 
  select(psqi_duration_c3, erqse_total_rap,erqse_total_sup, erqse_total_dis)

corr.test (hyp3_2)

### Sleep-Efficacy and ERF 

hyp3_3 <- df %>% 
  select(psqi_sf, erqf_total_rap,erqf_total_sup, erqdf_total_dis)

corr.test (hyp3_3)

### Sleep-Efficacy and ER-Selfefficacy 

hyp3_4 <- df %>% 
  select(psqi_sf, erqse_total_rap,erqse_total_sup, erqse_total_dis)

corr.test (hyp3_4)
```
################# THIS IS COOL SLEEP EFFICACY HAS TO DO WITH ER SUCCESS

```{r}
## Sleep Quality (PSQI) and Reacticity (PERS) 

cor.test (df$psqi_sf, df$pers_neg_total)
cor.test (df$psqi_sf, df$pers_pos_total)

cor.test(df$psqi_3_hour, df$pers_neg_total)
cor.test(df$psqi_3_hour, df$pers_pos_total)
```

