---
title: "winter_raw"
author: "Jonas Schöne"
date: "24 April 2019"
output: html_document
---

I included also attention check question in the first set, but before merging I will remove it.
in case someone is interested in excluding participants:

attention_1 

#
Library
#

```{r}
library(tidyverse)
library(readr)
```


###
Read raw-file_Winter
###

```{r}
dfraw <- read.csv2('D:/DownloadsDesktop/Desktop/Stanford/Bachelr-Thesis/WinterData/Winter19_Eligibility_Survey.csv',header =TRUE, sep =',')

```

## selecting relevant variables
Use the same order to select the data frame for the autumn data
```{r}
dfrawshort <- dfraw %>% 
  select(participant, age, race, gender, gender_other, starts_with("psqi"), starts_with("pers_") )
```

## Sleep Quality PSQI

```{r}
dfrawshort <- dfrawshort %>%
  mutate(psqi_1_hour_MT = psqi_1_hour + 12)

dfrawshort$psqi_1_hour_MT[dfrawshort$psqi_1_ampm == 'AM'] = dfrawshort$psqi_1_hour_MT[dfrawshort$psqi_1_ampm == 'AM'] - 12

dfrawshort <- dfrawshort

## transforming it into min since last midnight in order to avoid min/h calculation problems while substracting
## adding the min from another variable

dfrawshort$psqi_1_hour_MT_min = (dfrawshort$psqi_1_hour_MT *60) + dfrawshort$psqi_1_min


## to calculate the time slept until midnight (for example if someone felt asleep at 22:00, he slept 2h until mitnight and then I just add the minutes to the wake up), it will also be in minutes thats why 24 * 60 = 1440 ...lol

dfrawshort$psqi_timetillmidnight [dfrawshort$psqi_1_ampm == 'PM'] <-  (24*60) - dfrawshort$psqi_1_hour_MT_min [dfrawshort$psqi_1_ampm == 'PM']

##Sleep from midnight to morning RELEVANT FOR AM AND PM!!!

dfrawshort$psqi_timetillwakeup <- (dfrawshort$psqi_3_hour * 60) + dfrawshort$psqi_3_min

##Time spend in bed (PM) = time till midnight + time until wakey wakey 

dfrawshort$psqi_time_in_bed_pm <-  dfrawshort$psqi_timetillmidnight + dfrawshort$psqi_timetillwakeup 

## AM sleepers will be calculated by the difference between time until midnight when they fell asleep to their wake up

dfrawshort$psqi_timeaftermidnight [dfrawshort$psqi_1_ampm == 'AM'] <- dfrawshort$psqi_1_hour_MT

## time in bed wakeup time - time of falling asleep after midnight

dfrawshort$psqi_time_in_bed_am <- dfrawshort$psqi_timetillwakeup - dfrawshort$psqi_timeaftermidnight

## bringing am and pm together

dfrawshort <- dfrawshort %>%
  mutate(psqi_time_in_bed_min = case_when(
   dfrawshort$psqi_1_ampm == 'AM'~ dfrawshort$psqi_time_in_bed_am,
   dfrawshort$psqi_1_ampm == 'PM'~ dfrawshort$psqi_time_in_bed_pm
  ))

dfrawshort$psqi_time_in_bed_h <- dfrawshort$psqi_time_in_bed_min / 60

### COMPONENTS ########################
#####################

###Component 1: Subjective sleep quality-question 9 (for us psqi_6)

dfrawshort <- dfrawshort %>% 
  mutate(psqi_sq_c1 = case_when(
    dfrawshort$psqi_6 == "Very good"~ "0",
    dfrawshort$psqi_6 == "Fairly good"~ "1",
    dfrawshort$psqi_6 == "Fairly bad"~ "2",
    dfrawshort$psqi_6 == "Very bad"~ "3",
  ))

dfrawshort$psqi_sq_c1 <- as.numeric(dfrawshort$psqi_sq_c1)

###Component 2: Sleep latency-questions 2 and 5a

dfrawshort <- dfrawshort %>% 
  mutate(psqi_latency_a = case_when(
    dfrawshort$psqi_2 < 16 ~ "0",
    dfrawshort$psqi_2 > 15 & dfrawshort$psqi_2 < 31 ~ "1",
    dfrawshort$psqi_2 > 30 & dfrawshort$psqi_2 < 61 ~ "2",
    dfrawshort$psqi_2 > 60 ~ "3",
  ))

dfrawshort$psqi_latency_a <- as.numeric(dfrawshort$psqi_latency_a)

dfrawshort <- dfrawshort %>% 
  mutate(psqi_latency_b = case_when(
    dfrawshort$psqi_5a == "Less than once a week" ~ "1",
    dfrawshort$psqi_5a == "Not during the past month" ~ "0",
    dfrawshort$psqi_5a == "Once or twice a week" ~ "2",
    dfrawshort$psqi_5a == "Three or more times a week" ~ "3",
  ))

dfrawshort$psqi_latency_b <- as.numeric(dfrawshort$psqi_latency_b)

dfrawshort$psqi_latency_ab <- dfrawshort$psqi_latency_b + dfrawshort$psqi_latency_a

dfrawshort <- dfrawshort %>% 
  mutate(psqi_latency_c2 = case_when(
    dfrawshort$psqi_latency_ab == 0 ~ "0",
    dfrawshort$psqi_latency_ab > 0 & dfrawshort$psqi_latency_ab < 3 ~ "1",
    dfrawshort$psqi_latency_ab > 2 & dfrawshort$psqi_latency_ab < 5 ~ "2",
    dfrawshort$psqi_latency_ab > 4 ~ "3"
  ))

dfrawshort$psqi_latency_c2 <- as.numeric(dfrawshort$psqi_latency_c2)

####Component 3: Sleep duration-question 4

dfrawshort <- dfrawshort %>% 
  mutate(psqi_duration_c3 = case_when(
    dfrawshort$psqi_4 > 7 ~ "0",
    dfrawshort$psqi_4 < 8 & dfrawshort$psqi_4 > 5 ~ "1",
    dfrawshort$psqi_4 < 7 & dfrawshort$psqi_4 > 4 ~ "2",
    dfrawshort$psqi_4 < 5 ~ "3",
    dfrawshort$psqi_4 == "" ~ "-1",
  ))

dfrawshort$psqi_duration_c3 <- as.numeric(dfrawshort$psqi_duration_c3)
    


####Component 4: Sleep efficiency-questions 1, 3, and 4

## variable for % 
dfrawshort$psqi_sf <- (dfrawshort$psqi_4 / dfrawshort$psqi_time_in_bed_h) * 100

dfrawshort <- dfrawshort %>% 
  mutate(psqi_sf_c4 = case_when(
    dfrawshort$psqi_sf > 85 ~ 0,
    dfrawshort$psqi_sf > 74 & dfrawshort$psqi_sf < 85 ~ 1,
    dfrawshort$psqi_sf > 64 & dfrawshort$psqi_latency_ab < 75 ~ 2,
    dfrawshort$psqi_sf < 65 ~ 3
  ))

####Overall_Score

dfrawshort$psqi_total <- dfrawshort$psqi_sq_c1 + dfrawshort$psqi_latency_c2 + dfrawshort$psqi_duration_c3 + dfrawshort$psqi_sf_c4

dfrawshort %>% 
    select(starts_with("psqi"))

#### Visuals psqi

ggplot(dfrawshort, aes(x = dfrawshort$psqi_total)) + 
            geom_histogram( binwidth=1, color="black", fill="white")

```

```{r}
dfrawshort <- dfrawshort %>% 
  mutate(pers_1 = case_when(
    dfrawshort$pers_1 == "Very unlike me" ~ 1,
    dfrawshort$pers_1 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_1 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_1 == "Somewhat like me" ~ 4,
    dfrawshort$pers_1 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_2 = case_when(
    dfrawshort$pers_2 == "Very unlike me" ~ 1,
    dfrawshort$pers_2 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_2 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_2 == "Somewhat like me" ~ 4,
    dfrawshort$pers_2 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_3 = case_when(
    dfrawshort$pers_3 == "Very unlike me" ~ 1,
    dfrawshort$pers_3 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_3 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_3 == "Somewhat like me" ~ 4,
    dfrawshort$pers_3 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_4 = case_when(
    dfrawshort$pers_4 == "Very unlike me" ~ 1,
    dfrawshort$pers_4 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_4 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_4 == "Somewhat like me" ~ 4,
    dfrawshort$pers_4 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_5 = case_when(
    dfrawshort$pers_5 == "Very unlike me" ~ 1,
    dfrawshort$pers_5 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_5 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_5 == "Somewhat like me" ~ 4,
    dfrawshort$pers_5 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_6 = case_when(
    dfrawshort$pers_6 == "Very unlike me" ~ 1,
    dfrawshort$pers_6 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_6 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_6 == "Somewhat like me" ~ 4,
    dfrawshort$pers_6 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_7 = case_when(
    dfrawshort$pers_7 == "Very unlike me" ~ 1,
    dfrawshort$pers_7 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_7 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_7 == "Somewhat like me" ~ 4,
    dfrawshort$pers_7 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_8 = case_when(
    dfrawshort$pers_8 == "Very unlike me" ~ 1,
    dfrawshort$pers_8 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_8 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_8 == "Somewhat like me" ~ 4,
    dfrawshort$pers_8 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_9 = case_when(
    dfrawshort$pers_9 == "Very unlike me" ~ 1,
    dfrawshort$pers_9 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_9 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_9 == "Somewhat like me" ~ 4,
    dfrawshort$pers_9 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_10 = case_when(
    dfrawshort$pers_10 == "Very unlike me" ~ 1,
    dfrawshort$pers_10 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_10 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_10 == "Somewhat like me" ~ 4,
    dfrawshort$pers_10 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_11 = case_when(
    dfrawshort$pers_11 == "Very unlike me" ~ 1,
    dfrawshort$pers_11 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_11 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_11 == "Somewhat like me" ~ 4,
    dfrawshort$pers_11 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_12 = case_when(
    dfrawshort$pers_12 == "Very unlike me" ~ 1,
    dfrawshort$pers_12 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_12 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_12 == "Somewhat like me" ~ 4,
    dfrawshort$pers_12 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_13 = case_when(
    dfrawshort$pers_13 == "Very unlike me" ~ 1,
    dfrawshort$pers_13 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_13 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_13 == "Somewhat like me" ~ 4,
    dfrawshort$pers_13 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_14 = case_when(
    dfrawshort$pers_14 == "Very unlike me" ~ 1,
    dfrawshort$pers_14 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_14 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_14 == "Somewhat like me" ~ 4,
    dfrawshort$pers_14 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_15 = case_when(
    dfrawshort$pers_15 == "Very unlike me" ~ 1,
    dfrawshort$pers_15 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_15 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_15 == "Somewhat like me" ~ 4,
    dfrawshort$pers_15 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_16 = case_when(
    dfrawshort$pers_16 == "Very unlike me" ~ 1,
    dfrawshort$pers_16 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_16 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_16 == "Somewhat like me" ~ 4,
    dfrawshort$pers_16 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_17 = case_when(
    dfrawshort$pers_17 == "Very unlike me" ~ 1,
    dfrawshort$pers_17 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_17 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_17 == "Somewhat like me" ~ 4,
    dfrawshort$pers_17 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_18 = case_when(
    dfrawshort$pers_18 == "Very unlike me" ~ 1,
    dfrawshort$pers_18 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_18 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_18 == "Somewhat like me" ~ 4,
    dfrawshort$pers_18 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_19 = case_when(
    dfrawshort$pers_19 == "Very unlike me" ~ 1,
    dfrawshort$pers_19 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_19 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_19 == "Somewhat like me" ~ 4,
    dfrawshort$pers_19 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_20 = case_when(
    dfrawshort$pers_20 == "Very unlike me" ~ 1,
    dfrawshort$pers_20 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_20 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_20 == "Somewhat like me" ~ 4,
    dfrawshort$pers_20 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_21 = case_when(
    dfrawshort$pers_21 == "Very unlike me" ~ 1,
    dfrawshort$pers_21 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_21 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_21 == "Somewhat like me" ~ 4,
    dfrawshort$pers_21 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_22 = case_when(
    dfrawshort$pers_22 == "Very unlike me" ~ 1,
    dfrawshort$pers_22 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_22 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_22 == "Somewhat like me" ~ 4,
    dfrawshort$pers_22 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_23 = case_when(
    dfrawshort$pers_23 == "Very unlike me" ~ 1,
    dfrawshort$pers_23 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_23 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_23 == "Somewhat like me" ~ 4,
    dfrawshort$pers_23 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_24 = case_when(
    dfrawshort$pers_24 == "Very unlike me" ~ 1,
    dfrawshort$pers_24 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_24 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_24 == "Somewhat like me" ~ 4,
    dfrawshort$pers_24 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_25 = case_when(
    dfrawshort$pers_25 == "Very unlike me" ~ 1,
    dfrawshort$pers_25 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_25 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_25 == "Somewhat like me" ~ 4,
    dfrawshort$pers_25 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_26 = case_when(
    dfrawshort$pers_26 == "Very unlike me" ~ 1,
    dfrawshort$pers_26 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_26 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_26 == "Somewhat like me" ~ 4,
    dfrawshort$pers_26 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_27 = case_when(
    dfrawshort$pers_27 == "Very unlike me" ~ 1,
    dfrawshort$pers_27 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_27 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_27 == "Somewhat like me" ~ 4,
    dfrawshort$pers_27 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_28 = case_when(
    dfrawshort$pers_28 == "Very unlike me" ~ 1,
    dfrawshort$pers_28 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_28 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_28 == "Somewhat like me" ~ 4,
    dfrawshort$pers_28 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_29 = case_when(
    dfrawshort$pers_29 == "Very unlike me" ~ 1,
    dfrawshort$pers_29 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_29 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_29 == "Somewhat like me" ~ 4,
    dfrawshort$pers_29 == "Very like me" ~ 5,
  ))

dfrawshort <- dfrawshort %>% 
  mutate(pers_30 = case_when(
    dfrawshort$pers_30 == "Very unlike me" ~ 1,
    dfrawshort$pers_30 == "Somewhat unlike me" ~ 2,
    dfrawshort$pers_30 == "Neither like or unlike me"  ~ 3,
    dfrawshort$pers_30 == "Somewhat like me" ~ 4,
    dfrawshort$pers_30 == "Very like me" ~ 5,
  ))

#### General positive reactivity scale ####

## Positive-activation
dfrawshort$pers_pos_act <- (dfrawshort$pers_1 + dfrawshort$pers_7 + dfrawshort$pers_13 + dfrawshort$pers_19 + dfrawshort$pers_25)/5

## Positive-intensity
dfrawshort$pers_pos_int <- (dfrawshort$pers_5 + dfrawshort$pers_11 + dfrawshort$pers_17 + dfrawshort$pers_23 + dfrawshort$pers_29)/5

## Positive-duration
dfrawshort$pers_pos_dur <- (dfrawshort$pers_3 + dfrawshort$pers_9 + dfrawshort$pers_15 + dfrawshort$pers_27 + dfrawshort$pers_21)/5

##Positive Total

dfrawshort$pers_pos_total <- (dfrawshort$pers_pos_act + dfrawshort$pers_pos_int + dfrawshort$pers_pos_dur)/3

### General negative reactivity scale ###

### Negative-activation
dfrawshort$pers_neg_act <- (dfrawshort$pers_2 + dfrawshort$pers_8 + dfrawshort$pers_14 + dfrawshort$pers_20 + dfrawshort$pers_26)/5

### Negative-intensity
dfrawshort$pers_neg_int <- (dfrawshort$pers_6 + dfrawshort$pers_12 + dfrawshort$pers_18 + dfrawshort$pers_24 + dfrawshort$pers_30)/5

## Negative-duration
dfrawshort$pers_neg_dur <- (dfrawshort$pers_4 + dfrawshort$pers_10 + dfrawshort$pers_16 + dfrawshort$pers_22 + dfrawshort$pers_28)/5

## Negative Total

dfrawshort$pers_neg_total <- (dfrawshort$pers_neg_act + dfrawshort$pers_neg_int + dfrawshort$pers_neg_dur)/3

dfrawshort%>% 
    select(participant, starts_with("pers")) 
```
### rearrange new variables

```{r}
df_1 <- dfrawshort %>% 
  select(participant, age, race, gender, gender_other, starts_with("psqi"), starts_with("pers_") )
```

### produce output file without names that will be merged in next step lol
we will merge data_questionnaire_1 (select(participant, age, race, gender, gender_other, starts_with("psqi"), starts_with("pers_") ) ) with data_questionnaire_2 with this stuff

```{r}
write.csv(df_1, "data/data_questionnaire_2.csv")
```


##### END OF WINTER PREPROCESSING










###
Read raw-file_Spring
###

```{r}
yfraw <- read.csv2('D:/DownloadsDesktop/Desktop/Stanford/Bachelr-Thesis/WinterData/Spring_2019_Eligibility_Survey.csv',header =TRUE, sep =';')

```

## selecting relevant variables
Use the same order to select the data frame for the autumn data
```{r}
yfrawshort <- yfraw %>% 
  select(participant, age, race, gender, gender_other, starts_with("psqi"), starts_with("pers_") )
```

## Sleep Quality PSQI

```{r}
yfrawshort <- yfrawshort %>%
  mutate(psqi_1_hour_MT = psqi_1_hour + 12)

yfrawshort$psqi_1_hour_MT[yfrawshort$psqi_1_ampm == 'AM'] = yfrawshort$psqi_1_hour_MT[yfrawshort$psqi_1_ampm == 'AM'] - 12

yfrawshort <- yfrawshort

## transforming it into min since last midnight in order to avoid min/h calculation problems while substracting
## adding the min from another variable

yfrawshort$psqi_1_hour_MT_min = (yfrawshort$psqi_1_hour_MT *60) + yfrawshort$psqi_1_min


## to calculate the time slept until midnight (for example if someone felt asleep at 22:00, he slept 2h until mitnight and then I just add the minutes to the wake up), it will also be in minutes thats why 24 * 60 = 1440 ...lol

yfrawshort$psqi_timetillmidnight [yfrawshort$psqi_1_ampm == 'PM'] <-  (24*60) - yfrawshort$psqi_1_hour_MT_min [yfrawshort$psqi_1_ampm == 'PM']

##Sleep from midnight to morning RELEVANT FOR AM AND PM!!!

yfrawshort$psqi_timetillwakeup <- (yfrawshort$psqi_3_hour * 60) + yfrawshort$psqi_3_min

##Time spend in bed (PM) = time till midnight + time until wakey wakey 

yfrawshort$psqi_time_in_bed_pm <-  yfrawshort$psqi_timetillmidnight + yfrawshort$psqi_timetillwakeup 

## AM sleepers will be calculated by the difference between time until midnight when they fell asleep to their wake up

yfrawshort$psqi_timeaftermidnight [yfrawshort$psqi_1_ampm == 'AM'] <- yfrawshort$psqi_1_hour_MT

## time in bed wakeup time - time of falling asleep after midnight

yfrawshort$psqi_time_in_bed_am <- yfrawshort$psqi_timetillwakeup - yfrawshort$psqi_timeaftermidnight

## bringing am and pm together

yfrawshort <- yfrawshort %>%
  mutate(psqi_time_in_bed_min = case_when(
   yfrawshort$psqi_1_ampm == 'AM'~ yfrawshort$psqi_time_in_bed_am,
   yfrawshort$psqi_1_ampm == 'PM'~ yfrawshort$psqi_time_in_bed_pm
  ))

yfrawshort$psqi_time_in_bed_h <- yfrawshort$psqi_time_in_bed_min / 60

### COMPONENTS ########################
#####################

###Component 1: Subjective sleep quality-question 9 (for us psqi_6)

yfrawshort <- yfrawshort %>% 
  mutate(psqi_sq_c1 = case_when(
    yfrawshort$psqi_6 == "Very good"~ "0",
    yfrawshort$psqi_6 == "Fairly good"~ "1",
    yfrawshort$psqi_6 == "Fairly bad"~ "2",
    yfrawshort$psqi_6 == "Very bad"~ "3",
    yfrawshort$psqi_6 == "" ~ "-1",
  ))

yfrawshort$psqi_sq_c1 <- as.numeric(yfrawshort$psqi_sq_c1)

###Component 2: Sleep latency-questions 2 and 5a

yfrawshort <- yfrawshort %>% 
  mutate(psqi_latency_a = case_when(
    yfrawshort$psqi_2 < 16 ~ "0",
    yfrawshort$psqi_2 > 15 & yfrawshort$psqi_2 < 31 ~ "1",
    yfrawshort$psqi_2 > 30 & yfrawshort$psqi_2 < 61 ~ "2",
    yfrawshort$psqi_2 > 60 ~ "3",
    yfrawshort$psqi_2 == "" ~ "-1",
  ))

yfrawshort$psqi_latency_a <- as.numeric(yfrawshort$psqi_latency_a)

yfrawshort <- yfrawshort %>% 
  mutate(psqi_latency_b = case_when(
    yfrawshort$psqi_5a == "Less than once a week" ~ "1",
    yfrawshort$psqi_5a == "Not during the past month" ~ "0",
    yfrawshort$psqi_5a == "Once or twice a week" ~ "2",
    yfrawshort$psqi_5a == "Three or more times a week" ~ "3",
    yfrawshort$psqi_5a == "" ~ "-1",
  ))

yfrawshort$psqi_latency_b <- as.numeric(yfrawshort$psqi_latency_b)

yfrawshort$psqi_latency_ab <- yfrawshort$psqi_latency_b + yfrawshort$psqi_latency_a

yfrawshort <- yfrawshort %>% 
  mutate(psqi_latency_c2 = case_when(
    yfrawshort$psqi_latency_ab == 0 ~ "0",
    yfrawshort$psqi_latency_ab > 0 & yfrawshort$psqi_latency_ab < 3 ~ "1",
    yfrawshort$psqi_latency_ab > 2 & yfrawshort$psqi_latency_ab < 5 ~ "2",
    yfrawshort$psqi_latency_ab > 4 ~ "3"
  ))

yfrawshort$psqi_latency_c2 <- as.numeric(yfrawshort$psqi_latency_c2)

####Component 3: Sleep duration-question 4

yfrawshort <- yfrawshort %>% 
  mutate(psqi_duration_c3 = case_when(
    yfrawshort$psqi_4 > 7 ~ "0",
    yfrawshort$psqi_4 < 8 & yfrawshort$psqi_4 > 5 ~ "1",
    yfrawshort$psqi_4 < 7 & yfrawshort$psqi_4 > 4 ~ "2",
    yfrawshort$psqi_4 < 5 ~ "3",
    yfrawshort$psqi_4 == "" ~ "-1",
  ))

yfrawshort$psqi_duration_c3 <- as.numeric(yfrawshort$psqi_duration_c3)
    


####Component 4: Sleep efficiency-questions 1, 3, and 4

## variable for % 
yfrawshort$psqi_sf <- (yfrawshort$psqi_4 / yfrawshort$psqi_time_in_bed_h) * 100

yfrawshort <- yfrawshort %>% 
  mutate(psqi_sf_c4 = case_when(
    yfrawshort$psqi_sf > 85 ~ 0,
    yfrawshort$psqi_sf > 74 & yfrawshort$psqi_sf < 85 ~ 1,
    yfrawshort$psqi_sf > 64 & yfrawshort$psqi_latency_ab < 75 ~ 2,
    yfrawshort$psqi_sf < 65 ~ 3
  ))

####Overall_Score

yfrawshort$psqi_total <- yfrawshort$psqi_sq_c1 + yfrawshort$psqi_latency_c2 + yfrawshort$psqi_duration_c3 + yfrawshort$psqi_sf_c4

yfrawshort %>% 
    select(starts_with("psqi"))

#### Visuals psqi

ggplot(yfrawshort, aes(x = yfrawshort$psqi_total)) + 
            geom_histogram( binwidth=1, color="black", fill="white")

```

```{r}
yfrawshort <- yfrawshort %>% 
  mutate(pers_1 = case_when(
    yfrawshort$pers_1 == "Very unlike me" ~ 1,
    yfrawshort$pers_1 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_1 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_1 == "Somewhat like me" ~ 4,
    yfrawshort$pers_1 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_2 = case_when(
    yfrawshort$pers_2 == "Very unlike me" ~ 1,
    yfrawshort$pers_2 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_2 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_2 == "Somewhat like me" ~ 4,
    yfrawshort$pers_2 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_3 = case_when(
    yfrawshort$pers_3 == "Very unlike me" ~ 1,
    yfrawshort$pers_3 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_3 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_3 == "Somewhat like me" ~ 4,
    yfrawshort$pers_3 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_4 = case_when(
    yfrawshort$pers_4 == "Very unlike me" ~ 1,
    yfrawshort$pers_4 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_4 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_4 == "Somewhat like me" ~ 4,
    yfrawshort$pers_4 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_5 = case_when(
    yfrawshort$pers_5 == "Very unlike me" ~ 1,
    yfrawshort$pers_5 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_5 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_5 == "Somewhat like me" ~ 4,
    yfrawshort$pers_5 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_6 = case_when(
    yfrawshort$pers_6 == "Very unlike me" ~ 1,
    yfrawshort$pers_6 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_6 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_6 == "Somewhat like me" ~ 4,
    yfrawshort$pers_6 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_7 = case_when(
    yfrawshort$pers_7 == "Very unlike me" ~ 1,
    yfrawshort$pers_7 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_7 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_7 == "Somewhat like me" ~ 4,
    yfrawshort$pers_7 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_8 = case_when(
    yfrawshort$pers_8 == "Very unlike me" ~ 1,
    yfrawshort$pers_8 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_8 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_8 == "Somewhat like me" ~ 4,
    yfrawshort$pers_8 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_9 = case_when(
    yfrawshort$pers_9 == "Very unlike me" ~ 1,
    yfrawshort$pers_9 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_9 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_9 == "Somewhat like me" ~ 4,
    yfrawshort$pers_9 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_10 = case_when(
    yfrawshort$pers_10 == "Very unlike me" ~ 1,
    yfrawshort$pers_10 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_10 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_10 == "Somewhat like me" ~ 4,
    yfrawshort$pers_10 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_11 = case_when(
    yfrawshort$pers_11 == "Very unlike me" ~ 1,
    yfrawshort$pers_11 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_11 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_11 == "Somewhat like me" ~ 4,
    yfrawshort$pers_11 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_12 = case_when(
    yfrawshort$pers_12 == "Very unlike me" ~ 1,
    yfrawshort$pers_12 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_12 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_12 == "Somewhat like me" ~ 4,
    yfrawshort$pers_12 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_13 = case_when(
    yfrawshort$pers_13 == "Very unlike me" ~ 1,
    yfrawshort$pers_13 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_13 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_13 == "Somewhat like me" ~ 4,
    yfrawshort$pers_13 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_14 = case_when(
    yfrawshort$pers_14 == "Very unlike me" ~ 1,
    yfrawshort$pers_14 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_14 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_14 == "Somewhat like me" ~ 4,
    yfrawshort$pers_14 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_15 = case_when(
    yfrawshort$pers_15 == "Very unlike me" ~ 1,
    yfrawshort$pers_15 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_15 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_15 == "Somewhat like me" ~ 4,
    yfrawshort$pers_15 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_16 = case_when(
    yfrawshort$pers_16 == "Very unlike me" ~ 1,
    yfrawshort$pers_16 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_16 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_16 == "Somewhat like me" ~ 4,
    yfrawshort$pers_16 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_17 = case_when(
    yfrawshort$pers_17 == "Very unlike me" ~ 1,
    yfrawshort$pers_17 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_17 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_17 == "Somewhat like me" ~ 4,
    yfrawshort$pers_17 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_18 = case_when(
    yfrawshort$pers_18 == "Very unlike me" ~ 1,
    yfrawshort$pers_18 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_18 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_18 == "Somewhat like me" ~ 4,
    yfrawshort$pers_18 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_19 = case_when(
    yfrawshort$pers_19 == "Very unlike me" ~ 1,
    yfrawshort$pers_19 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_19 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_19 == "Somewhat like me" ~ 4,
    yfrawshort$pers_19 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_20 = case_when(
    yfrawshort$pers_20 == "Very unlike me" ~ 1,
    yfrawshort$pers_20 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_20 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_20 == "Somewhat like me" ~ 4,
    yfrawshort$pers_20 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_21 = case_when(
    yfrawshort$pers_21 == "Very unlike me" ~ 1,
    yfrawshort$pers_21 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_21 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_21 == "Somewhat like me" ~ 4,
    yfrawshort$pers_21 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_22 = case_when(
    yfrawshort$pers_22 == "Very unlike me" ~ 1,
    yfrawshort$pers_22 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_22 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_22 == "Somewhat like me" ~ 4,
    yfrawshort$pers_22 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_23 = case_when(
    yfrawshort$pers_23 == "Very unlike me" ~ 1,
    yfrawshort$pers_23 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_23 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_23 == "Somewhat like me" ~ 4,
    yfrawshort$pers_23 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_24 = case_when(
    yfrawshort$pers_24 == "Very unlike me" ~ 1,
    yfrawshort$pers_24 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_24 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_24 == "Somewhat like me" ~ 4,
    yfrawshort$pers_24 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_25 = case_when(
    yfrawshort$pers_25 == "Very unlike me" ~ 1,
    yfrawshort$pers_25 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_25 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_25 == "Somewhat like me" ~ 4,
    yfrawshort$pers_25 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_26 = case_when(
    yfrawshort$pers_26 == "Very unlike me" ~ 1,
    yfrawshort$pers_26 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_26 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_26 == "Somewhat like me" ~ 4,
    yfrawshort$pers_26 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_27 = case_when(
    yfrawshort$pers_27 == "Very unlike me" ~ 1,
    yfrawshort$pers_27 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_27 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_27 == "Somewhat like me" ~ 4,
    yfrawshort$pers_27 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_28 = case_when(
    yfrawshort$pers_28 == "Very unlike me" ~ 1,
    yfrawshort$pers_28 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_28 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_28 == "Somewhat like me" ~ 4,
    yfrawshort$pers_28 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_29 = case_when(
    yfrawshort$pers_29 == "Very unlike me" ~ 1,
    yfrawshort$pers_29 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_29 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_29 == "Somewhat like me" ~ 4,
    yfrawshort$pers_29 == "Very like me" ~ 5,
  ))

yfrawshort <- yfrawshort %>% 
  mutate(pers_30 = case_when(
    yfrawshort$pers_30 == "Very unlike me" ~ 1,
    yfrawshort$pers_30 == "Somewhat unlike me" ~ 2,
    yfrawshort$pers_30 == "Neither like or unlike me"  ~ 3,
    yfrawshort$pers_30 == "Somewhat like me" ~ 4,
    yfrawshort$pers_30 == "Very like me" ~ 5,
  ))

#### General positive reactivity scale ####

## Positive-activation
yfrawshort$pers_pos_act <- (yfrawshort$pers_1 + yfrawshort$pers_7 + yfrawshort$pers_13 + yfrawshort$pers_19 + yfrawshort$pers_25)/5

## Positive-intensity
yfrawshort$pers_pos_int <- (yfrawshort$pers_5 + yfrawshort$pers_11 + yfrawshort$pers_17 + yfrawshort$pers_23 + yfrawshort$pers_29)/5

## Positive-duration
yfrawshort$pers_pos_dur <- (yfrawshort$pers_3 + yfrawshort$pers_9 + yfrawshort$pers_15 + yfrawshort$pers_27 + yfrawshort$pers_21)/5

##Positive Total

yfrawshort$pers_pos_total <- (yfrawshort$pers_pos_act + yfrawshort$pers_pos_int + yfrawshort$pers_pos_dur)/3

### General negative reactivity scale ###

### Negative-activation
yfrawshort$pers_neg_act <- (yfrawshort$pers_2 + yfrawshort$pers_8 + yfrawshort$pers_14 + yfrawshort$pers_20 + yfrawshort$pers_26)/5

### Negative-intensity
yfrawshort$pers_neg_int <- (yfrawshort$pers_6 + yfrawshort$pers_12 + yfrawshort$pers_18 + yfrawshort$pers_24 + yfrawshort$pers_30)/5

## Negative-duration
yfrawshort$pers_neg_dur <- (yfrawshort$pers_4 + yfrawshort$pers_10 + yfrawshort$pers_16 + yfrawshort$pers_22 + yfrawshort$pers_28)/5

## Negative Total

yfrawshort$pers_neg_total <- (yfrawshort$pers_neg_act + yfrawshort$pers_neg_int + yfrawshort$pers_neg_dur)/3

yfrawshort%>% 
    select(participant, starts_with("pers")) 
```
### rearrange new variables

```{r}
yf_1 <- yfrawshort %>% 
  select(participant, age, race, gender, gender_other, starts_with("psqi"), starts_with("pers_") )
```



#### END OF SPRING PREPROCESSING








### produce output file without names that will be merged in next step lol
we will merge data_questionnaire_1 (select(participant, age, race, gender, gender_other, starts_with("psqi"), starts_with("pers_") ) ) with data_questionnaire_2 with this stuff

```{r}
write.csv(yf_1, "data/data_questionnaire_2.csv")
```

### loading the file that will be merged with

```{r}
df_2 <- read.csv(file= "data/data_questionnaire_1.csv")
```

### selecting relevant variables in the right order from second df

```{r}
df_2 <- df_2 %>% 
  select(participant, age, race, gender, gender_other, starts_with("psqi"), starts_with("pers_") )

df_all <- rbind(df_1, df_2)
df_all <- rbind(yf_1, df_all)

df_all$participant <- c (1:length(df_all$participant))
```

### print complete questionnaire

```{r}
write.csv(df_all, "data/data_questionnaire_complete.csv")
```

