---
title: "StatsStudy1Complete"
author: "Jonas Schöne"
date: "25 April 2019"
output: html_document
---

### library

```{r}
library(tidyverse)
library(psych)
library(GGally)
library(Hmisc)
library(kableExtra)
```


### load Data-File

```{r}
df1 <- read.csv("data/data_questionnaire_complete.csv")
```

### Filter 1 Case with a irregular bedtime, which is probably a missclick. Highly unlikely that a student goes to bed at 2PM.

### !!! The two excluded cases are most likely misclicks, because they also told that they sleep 6h. WHich only workes if you switch AM/PM

```{r}
df1 <- df1 %>% 
 filter(psqi_time_in_bed_h < 13)
```

## Getting a clean data frame
```{r}
# get the clean dataframe
df <- df1 %>% 
  filter(!is.na(psqi_sq_c1),!is.na(pers_neg_total), !is.na(pers_pos_total))
```

## Changing PSQI Efficacy values, which are over 100% to 100%

```{r}
df <- df %>% 
  mutate (psqi_sf = case_when(
    df$psqi_sf > 100 ~ 100,
    df$psqi_sf <= 100 ~ df$psqi_sf
    ))
```


### Demografics 

```{r}
### Age Distribution

ggplot(data = df,
       mapping = aes(x = age)) +
  geom_bar() 

describe(df$age)
sd(df$age, na.rm = FALSE)

describe.by(df$age, df$gender)

### Race 

table(df$race)

### Duration Calculated and Self-Reported

Calculated_Duration <- na.omit(df$psqi_time_in_bed_h)
hist(Calculated_Duration,prob=TRUE,main="Normal density + histogram")
  lines(density(Calculated_Duration),lty="dotted",col="red")
  
sd(df$psqi_time_in_bed_h, na.rm = FALSE)
mean(df$psqi_time_in_bed_h, na.rm = FALSE)
  
Self_Reported_Duration <- na.omit(df$psqi_4)
hist(Self_Reported_Duration,prob=TRUE,main="Normal density + histogram")
  lines(density(Self_Reported_Duration),lty="dotted",col="red")
  
sd(df$psqi_4, na.rm = FALSE)
mean(df$psqi_4, na.rm = FALSE)

cor.test(df$psqi_4, df$psqi_time_in_bed_h)
### Duration and Gender

ggplot(data = df,
       mapping = aes(x = df$gender,
                     y = df$psqi_time_in_bed_h,
                     ))+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  stat_summary(fun.y = "mean",
               geom = "point",
               color = "red")

### PSQI Components Gender

ggplot(data = df,
       mapping = aes(x = df$gender,
                     y = psqi_sq_c1,
                     ))+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  stat_summary(fun.y = "mean",
               geom = "point",
               color = "red")

ggplot(data = df,
       mapping = aes(x = df$gender,
                     y = psqi_latency_c2,
                     ))+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  stat_summary(fun.y = "mean",
               geom = "point",
               color = "red")

ggplot(data = df,
       mapping = aes(x = df$gender,
                     y = df$psqi_time_in_bed_h,
                     ))+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  stat_summary(fun.y = "mean",
               geom = "point",
               color = "red")

ggplot(data = df,
       mapping = aes(x = df$gender,
                     y = psqi_sf,
                     ))+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  stat_summary(fun.y = "mean",
               geom = "point",
               color = "red")

SleepQualityDes <- describe(df$psqi_sq_c1)
SleepLatencyDes <- describe(df$psqi_latency_c2)
SleepDurationDes <- describe(df$psqi_duration_c3)
SleepEffeciencyDes <- describe(df$psqi_sf)

DistrPSQIGender <- describeBy (df$psqi_total,group = df$gender)

### distribution of PSQI scores
PSQItotalMean <- df$psqi_total/4
PSQItotalDes <- describe(PSQItotalMean)

ggplot(data = df,
       mapping = aes(x = PSQItotalMean)) +
  geom_density() 


# tempx <- na.omit(df$psqi_total)
# tempx <- tempx / 4
# hist(x,prob=TRUE,main="Normal density + histogram")
#   lines(density(x),lty="dotted",col="red")
                     
```
#### Tests

```{r}
###Test

ggplot(df, aes(x = psqi_total))+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, fill="red") 

```

### Item Analysis PSQI

```{r}
### Selecting Items
psqi.df <- df %>% 
  select(psqi_sq_c1,psqi_latency_c2,psqi_duration_c3,psqi_sf_c4)

### Componenten Consistency

alpha(psqi.df)

describe(psqi.df)

### intercorrelation

ggpairs(df %>% 
  select(psqi_sq_c1, psqi_latency_c2, psqi_time_in_bed_h, psqi_sf))

### distribution PSQI_total
PSQI_Total <- df$psqi_total / 4

ggplot(df, aes(x = PSQI_Total))+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, fill="red")

sd(PSQI_Total, na.rm = FALSE)
mean(PSQI_Total, na.rm = FALSE)

sd(df$psqi_2, na.rm = FALSE)
mean(df$psqi_2, na.rm = FALSE)

sd(df$psqi_sq_c1, na.rm = FALSE)
mean(df$psqi_sq_c1, na.rm = FALSE)

sd(df$psqi_sf, na.rm = FALSE)
mean(df$psqi_sf, na.rm = FALSE)

sd(df$psqi_4, na.rm = FALSE)
mean(df$psqi_4, na.rm = FALSE)

```
### 1 Component PSQI

```{r}
### PSQI 1 and NEG
ggplot(data = df, mapping = aes(x = psqi_sq_c1, y = pers_neg_total)) +
  geom_point() +
  geom_smooth(method = "lm")

tmp2 <- lm(df$pers_neg_total ~ df$psqi_sq_c1, data = df)
summary(tmp2)

### which part is contributes to that relationship most (IT IS INTENSITY)

tmp3 <- lm(df$psqi_sq_c1 ~df$pers_neg_act + df$pers_neg_dur + df$pers_neg_int, data = df)
summary(tmp3)

tmp7 <- lm(df$pers_neg_dur ~ df$psqi_sq_c1, data = df)
summary(tmp7)

tmp4 <- lm(df$pers_neg_act ~ df$psqi_sq_c1, data = df)
summary(tmp4)

tmp8 <- lm(df$pers_neg_int ~ df$psqi_sq_c1, data = df)
summary(tmp8)

### PSQI Pos

ggplot(data = df, mapping = aes(x = psqi_sq_c1, y = pers_pos_total)) +
  geom_point() +
  geom_smooth(method = "lm")

tmp3 <- lm(df$psqi_sq_c1 ~df$pers_pos_act + df$pers_pos_dur + df$pers_pos_int, data = df)
summary(tmp3)

tmp4 <- lm(df$pers_pos_total ~ df$psqi_sq_c1, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_dur ~ df$psqi_sq_c1, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_act ~ df$psqi_sq_c1, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_int ~ df$psqi_sq_c1, data = df)
summary(tmp4)

```
### Component 2 Latency

```{r}
### PSQI 2 and NEG
ggplot(data = df, mapping = aes(x = psqi_latency_c2, y = pers_neg_total)) +
  geom_point() +
  geom_smooth(method = "lm")

tmp2 <- lm(df$pers_neg_total ~ df$psqi_latency_c2, data = df)
summary(tmp2)

### which part is contributes to that relationship most (IT IS INTENSITY)

tmp3 <- lm(df$psqi_latency_c2 ~df$pers_neg_act + df$pers_neg_dur + df$pers_neg_int, data = df)
summary(tmp3)

tmp7 <- lm(df$pers_neg_dur ~ df$psqi_latency_c2, data = df)
summary(tmp7)

tmp4 <- lm(df$pers_neg_act ~ df$psqi_latency_c2, data = df)
summary(tmp4)

tmp8 <- lm(df$pers_neg_int ~ df$psqi_latency_c2, data = df)
summary(tmp8)

### PSQI Pos

ggplot(data = df, mapping = aes(x = psqi_latency_c2, y = pers_pos_total)) +
  geom_point() +
  geom_smooth(method = "lm")

### which part is contributes to that relationship most (IT IS INTENSITY)

tmp3 <- lm(df$psqi_latency_c2 ~df$pers_pos_act + df$pers_pos_dur + df$pers_pos_int, data = df)
summary(tmp3)

tmp4 <- lm(df$pers_pos_total ~ df$psqi_latency_c2, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_dur ~ df$psqi_latency_c2, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_act ~ df$psqi_latency_c2, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_int ~ df$psqi_latency_c2, data = df)
summary(tmp4)
```
### 3.Componente Duration

```{r}
### PSQI 3 and NEG
ggplot(data = df, mapping = aes(x = psqi_4, y = pers_neg_total)) +
  geom_point() +
  geom_smooth(method = "lm")

tmp2 <- lm(df$pers_neg_total ~ df$psqi_time)
summary(tmp2)

### which part is contributes to that relationship most (IT IS INTENSITY)

tmp3 <- lm(df$psqi_4 ~df$pers_neg_act + df$pers_neg_dur + df$pers_neg_int, data = df)
summary(tmp3)

tmp7 <- lm(df$pers_neg_dur ~ df$psqi_time, data = df)
summary(tmp7)

tmp4 <- lm(df$pers_neg_act ~ df$psqi_4, data = df)
summary(tmp4)

tmp8 <- lm(df$pers_neg_int ~ df$psqi_4, data = df)
summary(tmp8)

### PSQI Pos

ggplot(data = df, mapping = aes(x = psqi_4, y = pers_pos_total)) +
  geom_point() +
  geom_smooth(method = "lm")

### which part is contributes to that relationship most (IT IS INTENSITY)

tmp3 <- lm(df$psqi_4 ~ df$pers_pos_act + df$pers_pos_dur + df$pers_pos_int, data = df)
summary(tmp3)

tmp4 <- lm(df$pers_pos_total ~ df$psqi_4, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_dur ~ df$psqi_4, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_act ~ df$psqi_4, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_int ~ df$psqi_4, data = df)
summary(tmp4)

## CORRELATION BETWEEN REPORTED AND CALCULATED DURATION

tmp2 <- lm(df$psqi_time_in_bed_h ~ df$psqi_4, data = df)
summary(tmp2)

# r^2 = .145 
```
### Sleep Efficancy

```{r}

### PSQI 4 and NEG
ggplot(data = df, mapping = aes(x = psqi_sf, y = pers_neg_total)) +
  geom_point() +
  geom_smooth(method = "lm")

tmp2 <- lm(df$pers_neg_total ~ df$psqi_sf, data = df)
summary(tmp2)

### which part is contributes to that relationship most (IT IS INTENSITY)

tmp3 <- lm(df$psqi_sf ~df$pers_neg_act + df$pers_neg_dur + df$pers_neg_int, data = df)
summary(tmp3)

tmp7 <- lm(df$pers_neg_dur ~ df$psqi_sf, data = df)
summary(tmp7)

tmp4 <- lm(df$pers_neg_act ~ df$psqi_sf, data = df)
summary(tmp4)

tmp8 <- lm(df$pers_neg_int ~ df$psqi_sf, data = df)
summary(tmp8)

### PSQI Pos

ggplot(data = df, mapping = aes(x = psqi_sf, y = pers_pos_total)) +
  geom_point() +
  geom_smooth(method = "lm")

### which part is contributes to that relationship most (IT IS INTENSITY)

tmp3 <- lm(df$psqi_sf ~ df$pers_pos_act + df$pers_pos_dur + df$pers_pos_int, data = df)
summary(tmp3)

tmp4 <- lm(df$pers_pos_total ~ df$psqi_sf, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_dur ~ df$psqi_sf, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_act ~ df$psqi_sf, data = df)
summary(tmp4)

tmp4 <- lm(df$pers_pos_int ~ df$psqi_sf, data = df)
summary(tmp4)

```
###Item analyse PERS

```{r}
### Componenten Consistency
PERSpos.df <- df %>%  
  select(starts_with("pers_pos"), - pers_pos_total)

alpha(PERSpos.df)

PERSneg.df <- df %>% 
  select(starts_with("pers_neg"), - pers_neg_total) 
  
alpha(PERSneg.df)

PERS.df <- df %>% 
  select(participant, starts_with("pers_pos"), starts_with("pers_neg"))

describe(PERS.df)

### intercorrelation

ggpairs(df %>% 
  select(pers_pos_act, pers_pos_dur, pers_pos_int, pers_pos_total))

ggpairs(df %>% 
  select(pers_neg_act, pers_neg_dur, pers_neg_int, pers_neg_total))

sd(df$pers_neg_total, na.rm = FALSE)
mean(df$pers_neg_total, na.rm = FALSE)

sd(df$pers_pos_total, na.rm = FALSE)
mean(df$pers_pos_total, na.rm = FALSE)
```



### correlation stuff PSQI (Sleep Quality) and Reactivity (PERS)

```{r}

ggpairs(df %>% 
  select(psqi_sq_c1, psqi_latency_c2, psqi_4, psqi_sf, pers_pos_total, pers_neg_total))


```

```{r}

# linear regression for standardized coefficients
lm(scale(pers_neg_total) ~ scale(psqi_sq_c1) + scale(psqi_latency_c2) + scale(psqi_4),data = df) %>% summary()

lm(scale(pers_pos_total) ~ scale(psqi_sq_c1) + scale(psqi_latency_c2) + scale(psqi_4),data = df) %>% summary()



anorex.1 <- lm(pers_neg_total ~ psqi_sq_c1 + psqi_latency_c2 + psqi_4 + psqi_sf ,data = df)
summary(anorex.1)

ggplot(data = df, mapping = aes(x = psqi_sf + psqi_latency_c2 + psqi_4 + psqi_sf, y = pers_neg_total)) +
  geom_point() +
  geom_smooth(method = "lm")

anorex.2 <- lm(df$pers_pos_total ~ df$psqi_sq_c1 + psqi_latency_c2 + psqi_4 + psqi_sf ,data = df)
summary(anorex.2)

ggplot(data = df, mapping = aes(x = psqi_sf + psqi_latency_c2 + psqi_4 + psqi_sf, y = pers_pos_total)) +
  geom_point() +
  geom_smooth(method = "lm")
```

### OVerview o correlations for entry in article

```{r}
ov <- df %>%
  select(psqi_total , psqi_sq_c1 , psqi_latency_c2 , psqi_4 , psqi_sf, pers_neg_total,pers_pos_total )

corr.test(ov)
```

